---
title: "Group_Project"
author: "Trisha, Kathie, E-anna"
date: "2023-12-05"
output: html_document
---
### library 
```{r}
library(readr)
library(tidyr)
library(stringr)
library(ggplot2)
library(dplyr)
library(knitr)
```

### load data sets 
```{r}

list.files("data")

degrees_awarded_by_identity <- read.csv("data/PCHEES_Dashboard_-_Degrees_Awarded_by identity.csv") %>%
  rename(Academic_Year = "AcademicYear", Student_Type = "Student.Type", 
         Demographic_Group = "DemographicGroup", 
         Demographic_Value = "DemographicValue", 
         Demographic_Subgroup = "DemographicSubgroup", 
         Demographic_Subgroup_Value = "DemographicSubgroupValue",
         Number_of_Degrees = "Number.of.Degrees", 
         Percent_of_Group = "pctOfGroup", 
         Percent_of_Subgroup = "pctOfSubgroup") 

degrees_by_major <- read.csv("data/PCHEES_Dashboard_-_Degrees_by_Major.csv") %>%
  rename(Academic_Year = "AcademicYear", Award_Level = "AwardLevel") %>%
  select(Academic_Year, Institution, Award_Level, TwoDigitCIPDescription, 
         TotalDegrees, STEM)
```
### graph statewide STEM degrees granted in general
```{r}
degrees_by_major_v1 <- degrees_by_major %>%
  select(Academic_Year, Institution, Award_Level, STEM, TotalDegrees) %>%
  group_by(Academic_Year, Institution) %>%
  summarize(Graduate_STEM = sum(TotalDegrees[Award_Level == "Graduate" & STEM]),
            Graduate_NonSTEM = sum(TotalDegrees[Award_Level == "Graduate" & !STEM]),
            Undergraduate_STEM = sum(TotalDegrees[Award_Level == "Undergraduate" & STEM]),
            Undergraduate_NonSTEM = sum(TotalDegrees[Award_Level == "Undergraduate" & !STEM])) %>%
  mutate(Academic_Start_Year = as.integer(substring(Academic_Year, 1, 4)))
  
degrees_by_major_statewide <- degrees_by_major_v1 %>%
  ungroup() %>%
  filter(Institution == "Statewide")
# sub string extracts the first four numbers of each unit in academic year

ggplot(degrees_by_major_statewide, aes(x = Academic_Start_Year)) +
  geom_line(aes(y = Graduate_STEM, color = "Graduate_STEM")) +
  geom_line(aes(y = Graduate_NonSTEM, color = "Graduate_NonSTEM")) +
  geom_line(aes(y = Undergraduate_STEM, color = "Undergraduate_STEM")) +
  geom_line(aes(y = Undergraduate_NonSTEM, color = "Undergraduate_NonSTEM")) +
  labs(title = "Degrees Granted in Washington State",
    x = "Academic Year", y = "Number of Degrees Granted", color = "Major Type")
```

#### Undergrad STEM Degrees by University
```{r}
uni_undergrad_STEM <- degrees_by_major_v1 %>%
  filter(Institution != "Statewide") %>%
  group_by(Institution) %>%
  select(Academic_Year, Institution, Undergraduate_STEM, Academic_Start_Year)

ggplot(uni_undergrad_STEM, aes(x = Academic_Start_Year, y = Undergraduate_STEM,
                               color = Institution)) +
  geom_line() +
  labs(title = "Undergraduate STEM Degrees Granted", x = "Academic Year",
       y = "Number of Degrees Granted", color = "University")
```

#### Undergrad NonSTEM Degrees by University
```{r}
uni_undergrad_NonSTEM <- degrees_by_major_v1 %>%
  filter(Institution != "Statewide") %>%
  group_by(Institution) %>%
  select(Academic_Year, Institution, Undergraduate_NonSTEM, Academic_Start_Year)

ggplot(uni_undergrad_NonSTEM, aes(x = Academic_Start_Year, y = Undergraduate_NonSTEM,
                               color = Institution)) +
  geom_line() +
  labs(title = "Undergraduate Non-STEM Degrees Granted", x = "Academic Year",
       y = "Number of Degrees Granted", color = "University")
```


#### Graduate STEM Degrees by University
```{r}
uni_grad_STEM <- degrees_by_major_v1 %>%
  filter(Institution != "Statewide") %>%
  group_by(Institution) %>%
  select(Academic_Year, Institution, Graduate_STEM, Academic_Start_Year)

ggplot(uni_grad_STEM, aes(x = Academic_Start_Year, y = Graduate_STEM,
                               color = Institution)) +
  geom_line() +
  labs(title = "Graduate STEM Degrees Granted", x = "Academic Year",
       y = "Number of Degrees Granted", color = "University")
```


#### Graduate Non STEM Degrees by University
```{r}
uni_grad_NonSTEM <- degrees_by_major_v1 %>%
  filter(Institution != "Statewide") %>%
  group_by(Institution) %>%
  select(Academic_Year, Institution, Graduate_NonSTEM, Academic_Start_Year)

ggplot(uni_grad_NonSTEM, aes(x = Academic_Start_Year, y = Graduate_NonSTEM,
                               color = Institution)) +
  geom_line() +
  labs(title = "Graduate Non-STEM Degrees Granted", x = "Academic Year",
       y = "Number of Degrees Granted", color = "University")
```

#### major degrees granted by race/ethnicity 
```{r}
degrees_by_identity_clean <- degrees_awarded_by_identity %>%
  filter(Demographic_Group == "STEM Status" & Demographic_Subgroup == "Race/Ethnicity") %>%
  mutate(Academic_Start_Year = as.integer(substring(Academic_Year, 1, 4))) %>%
  select(Academic_Year, Academic_Start_Year, Institution, Student_Type, 
         Demographic_Value, Demographic_Subgroup_Value, Number_of_Degrees,
         Percent_of_Group, Percent_of_Subgroup)
```

#### Statewide Degrees overtime by Race and Ethnicity
```{r}
All_STEM_Race <- degrees_by_identity_clean %>%
  filter(Demographic_Value == "STEM") %>%
  filter(Demographic_Subgroup_Value == "White"| 
         Demographic_Subgroup_Value == "Black"|
         Demographic_Subgroup_Value == "Asian"| 
         Demographic_Subgroup_Value == "Asian/Native Hawaiian or Other Pacific Islander"|
         Demographic_Subgroup_Value == "Multi Racial"|
         Demographic_Subgroup_Value == "Hispanic"|
         Demographic_Subgroup_Value == "Unknown")

All_NonSTEM_Race <- degrees_by_identity_clean %>%
  filter(Demographic_Value == "Not STEM") %>%
  filter(Demographic_Subgroup_Value == "White"| 
         Demographic_Subgroup_Value == "Black"|
         Demographic_Subgroup_Value == "Asian"| 
         Demographic_Subgroup_Value == "Asian/Native Hawaiian or Other Pacific Islander"|
         Demographic_Subgroup_Value == "Multi Racial"|
         Demographic_Subgroup_Value == "Hispanic"|
         Demographic_Subgroup_Value == "Unknown")

Black_STEM <- All_STEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Black") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(black_nodg = "Number_of_Degrees_Graduate", 
         black_pgg = "Percent_of_Group_Graduate",
         black_nodug = "Number_of_Degrees_Undergraduate", 
         black_pgug = "Percent_of_Group_Undergraduate")
  
Black_NonSTEM <- All_NonSTEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Black") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(black_nodg = "Number_of_Degrees_Graduate", 
         black_pgg = "Percent_of_Group_Graduate",
         black_nodug = "Number_of_Degrees_Undergraduate", 
         black_pgug = "Percent_of_Group_Undergraduate")

White_STEM <- All_STEM_Race %>% 
  filter(Demographic_Subgroup_Value == "White") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(white_nodg = "Number_of_Degrees_Graduate", 
         white_pgg = "Percent_of_Group_Graduate",
         white_nodug = "Number_of_Degrees_Undergraduate", 
         white_pgug = "Percent_of_Group_Undergraduate")

White_NonSTEM <- All_NonSTEM_Race %>% 
  filter(Demographic_Subgroup_Value == "White") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(white_nodg = "Number_of_Degrees_Graduate", 
         white_pgg = "Percent_of_Group_Graduate",
         white_nodug = "Number_of_Degrees_Undergraduate", 
         white_pgug = "Percent_of_Group_Undergraduate")


AAPI_STEM <- All_STEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Asian/Native Hawaiian or Other Pacific Islander") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(aapi_nodg = "Number_of_Degrees_Graduate", 
         aapi_pgg = "Percent_of_Group_Graduate",
         aapi_nodug = "Number_of_Degrees_Undergraduate", 
         aapi_pgug = "Percent_of_Group_Undergraduate")

AAPI_NonSTEM <- All_NonSTEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Asian/Native Hawaiian or Other Pacific Islander") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(aapi_nodg = "Number_of_Degrees_Graduate", 
         aapi_pgg = "Percent_of_Group_Graduate",
         aapi_nodug = "Number_of_Degrees_Undergraduate", 
         aapi_pgug = "Percent_of_Group_Undergraduate")

Multi_STEM <- All_STEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Multi Racial") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(multi_nodg = "Number_of_Degrees_Graduate", 
         multi_pgg = "Percent_of_Group_Graduate",
         multi_nodug = "Number_of_Degrees_Undergraduate", 
         multi_pgug = "Percent_of_Group_Undergraduate")

Multi_NonSTEM <- All_NonSTEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Multi Racial") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(multi_nodg = "Number_of_Degrees_Graduate", 
         multi_pgg = "Percent_of_Group_Graduate",
         multi_nodug = "Number_of_Degrees_Undergraduate", 
         multi_pgug = "Percent_of_Group_Undergraduate")

Hispanic_STEM <- All_STEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Hispanic") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(hisp_nodg = "Number_of_Degrees_Graduate", 
         hisp_pgg = "Percent_of_Group_Graduate",
         hisp_nodug = "Number_of_Degrees_Undergraduate", 
         hisp_pgug = "Percent_of_Group_Undergraduate")

Hispanic_NonSTEM <- All_NonSTEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Hispanic") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(hisp_nodg = "Number_of_Degrees_Graduate", 
         hisp_pgg = "Percent_of_Group_Graduate",
         hisp_nodug = "Number_of_Degrees_Undergraduate", 
         hisp_pgug = "Percent_of_Group_Undergraduate")

Unknown_STEM <- All_STEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Unknown") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(uk_nodg = "Number_of_Degrees_Graduate", 
         uk_pgg = "Percent_of_Group_Graduate",
         uk_nodug = "Number_of_Degrees_Undergraduate", 
         uk_pgug = "Percent_of_Group_Undergraduate")

Unknown_NonSTEM  <- All_NonSTEM_Race %>% 
  filter(Demographic_Subgroup_Value == "Unknown") %>%
  select(Academic_Start_Year, Institution, Number_of_Degrees, Percent_of_Group, 
         Demographic_Subgroup_Value, Student_Type) %>%
  pivot_wider(id_cols = c(Academic_Start_Year, Institution, 
                          Demographic_Subgroup_Value),
              names_from = Student_Type,
              values_from = c(Number_of_Degrees, Percent_of_Group)) %>%
  rename(uk_nodg = "Number_of_Degrees_Graduate", 
         uk_pgg = "Percent_of_Group_Graduate",
         uk_nodug = "Number_of_Degrees_Undergraduate", 
         uk_pgug = "Percent_of_Group_Undergraduate")
```

#### Filter Statewide 
```{r}
Black_STEM_statewide <- Black_STEM %>%
  filter(Institution == "Statewide")
  
Black_NonSTEM_statewide <- Black_NonSTEM %>%
  filter(Institution == "Statewide")

White_STEM_statewide <- White_STEM %>%
  filter(Institution == "Statewide")

White_NonSTEM_statewide <- White_NonSTEM %>%
  filter(Institution == "Statewide")


AAPI_STEM_statewide <- AAPI_STEM %>%
  filter(Institution == "Statewide")

AAPI_NonSTEM_statewide <- AAPI_NonSTEM %>%
  filter(Institution == "Statewide")

Multi_STEM_statewide <- Multi_STEM %>%
  filter(Institution == "Statewide")

Multi_NonSTEM_statewide <- Multi_NonSTEM %>%
  filter(Institution == "Statewide")

Hispanic_STEM_statewide <- Hispanic_STEM %>%
  filter(Institution == "Statewide")

Hispanic_NonSTEM_statewide <- Hispanic_NonSTEM %>%
  filter(Institution == "Statewide")

Unknown_STEM_statewide <- Unknown_STEM %>%
  filter(Institution == "Statewide")

Unknown_NonSTEM_statewide <- Unknown_NonSTEM %>%
  filter(Institution == "Statewide")
```

#### Students with STEM Degrees Statewide by Race/Ethnicity
```{r}
statewide_STEM_degrees_by_race <- degrees_by_major_statewide %>%
  inner_join(Black_STEM_statewide, by = "Academic_Start_Year") %>%
  inner_join(White_STEM_statewide, by = "Academic_Start_Year") %>%
  inner_join(AAPI_STEM_statewide, by = "Academic_Start_Year") %>%
  inner_join(Multi_STEM_statewide, by = "Academic_Start_Year") %>%
  inner_join(Hispanic_STEM_statewide, by = "Academic_Start_Year") %>%
  inner_join(Unknown_STEM_statewide, by = "Academic_Start_Year") %>%
  select(Academic_Start_Year, Graduate_STEM, Undergraduate_STEM, black_nodg,
         black_nodug, white_nodug, white_nodg, aapi_nodug, aapi_nodg,
         multi_nodug, multi_nodg, hisp_nodug, hisp_nodg, uk_nodg, uk_nodug)

ggplot(statewide_STEM_degrees_by_race, aes(x = Academic_Start_Year)) +
  geom_line(aes(y = Undergraduate_STEM, color = "Overall")) +
  geom_line(aes(y = black_nodug, color = "Black")) +
  geom_line(aes(y = white_nodug, color = "White")) +
  geom_line(aes(y = aapi_nodug, color = "AAPI")) +
  geom_line(aes(y = multi_nodug, color = "Multi Racial")) +
  geom_line(aes(y = hisp_nodug, color = "Hispanic")) +
  geom_line(aes(y = uk_nodug, color = "Unknown")) +
  labs(title = "Undergraduate Degrees Granted by Race/Ethnicity in Washington State",
       x = "Academic Year",
       y = "Number of Degrees Granted",
       color = "Race/Ethnicity")
```

#### UW
```{r}
Black_STEM_UW <- Black_STEM %>%
  filter(Institution == "University of Washington")
  
Black_NonSTEM_UW <- Black_NonSTEM %>%
  filter(Institution == "University of Washington")

White_STEM_UW <- White_STEM %>%
  filter(Institution == "University of Washington")

White_NonSTEM_UW <- White_NonSTEM %>%
  filter(Institution == "University of Washington")


AAPI_STEM_UW <- AAPI_STEM %>%
  filter(Institution == "University of Washington")

AAPI_NonSTEM_UW <- AAPI_NonSTEM %>%
  filter(Institution == "University of Washington")

Multi_STEM_UW <- Multi_STEM %>%
  filter(Institution == "University of Washington")

Multi_NonSTEM_UW <- Multi_NonSTEM %>%
  filter(Institution == "University of Washington")

Hispanic_STEM_UW <- Hispanic_STEM %>%
  filter(Institution == "University of Washington")

Hispanic_NonSTEM_UW <- Hispanic_NonSTEM %>%
  filter(Institution == "University of Washington")

Unknown_STEM_UW <- Unknown_STEM %>%
  filter(Institution == "University of Washington")

Unknown_NonSTEM_UW <- Unknown_NonSTEM %>%
  filter(Institution == "University of Washington")

UW_degrees_by_major <- degrees_by_major_v1 %>%
  filter(Institution == "University of Washington")

UW_STEM_degrees_by_race <- UW_degrees_by_major %>%
  inner_join(Black_STEM_UW, by = "Academic_Start_Year") %>%
  inner_join(White_STEM_UW, by = "Academic_Start_Year") %>%
  inner_join(AAPI_STEM_UW, by = "Academic_Start_Year") %>%
  inner_join(Multi_STEM_UW, by = "Academic_Start_Year") %>%
  inner_join(Hispanic_STEM_UW, by = "Academic_Start_Year") %>%
  inner_join(Unknown_STEM_UW, by = "Academic_Start_Year") %>%
  select(Academic_Start_Year, Graduate_STEM, Undergraduate_STEM, black_nodg,
         black_nodug, white_nodug, white_nodg, aapi_nodug, aapi_nodg,
         multi_nodug, multi_nodg, hisp_nodug, hisp_nodg, uk_nodg, uk_nodug)

ggplot(UW_STEM_degrees_by_race, aes(x = Academic_Start_Year)) +
  geom_line(aes(y = black_nodug, color = "Black")) +
  geom_line(aes(y = white_nodug, color = "White")) +
  geom_line(aes(y = aapi_nodug, color = "AAPI")) +
  geom_line(aes(y = multi_nodug, color = "Multi Racial")) +
  geom_line(aes(y = hisp_nodug, color = "Hispanic")) +
  geom_line(aes(y = uk_nodug, color = "Unknown")) +
  labs(title = "Undergraduate STEM Degrees Granted by Race/Ethnicity at UW",
       x = "Academic Year",
       y = "Number of Degrees Granted",
       color = "Race/Ethnicity")
```

#### WSU
```{r}
Black_STEM_WSU <- Black_STEM %>%
  filter(Institution == "Washington State University")
  
Black_NonSTEM_WSU <- Black_NonSTEM %>%
  filter(Institution == "Washington State University")

White_STEM_WSU <- White_STEM %>%
  filter(Institution == "Washington State University")

White_NonSTEM_WSU <- White_NonSTEM %>%
  filter(Institution == "Washington State University")


AAPI_STEM_WSU <- AAPI_STEM %>%
  filter(Institution == "Washington State University")

AAPI_NonSTEM_WSU <- AAPI_NonSTEM %>%
  filter(Institution == "Washington State University")

Multi_STEM_WSU <- Multi_STEM %>%
  filter(Institution == "Washington State University")

Multi_NonSTEM_WSU <- Multi_NonSTEM %>%
  filter(Institution == "Washington State University")

Hispanic_STEM_WSU <- Hispanic_STEM %>%
  filter(Institution == "Washington State University")

Hispanic_NonSTEM_WSU <- Hispanic_NonSTEM %>%
  filter(Institution == "Washington State University")

Unknown_STEM_WSU <- Unknown_STEM %>%
  filter(Institution == "Washington State University")

Unknown_NonSTEM_WSU <- Unknown_NonSTEM %>%
  filter(Institution == "Washington State University")

WSU_degrees_by_major <- degrees_by_major_v1 %>%
  filter(Institution == "Washington State University")

WSU_STEM_degrees_by_race <- WSU_degrees_by_major %>%
  inner_join(Black_STEM_WSU, by = "Academic_Start_Year") %>%
  inner_join(White_STEM_WSU, by = "Academic_Start_Year") %>%
  inner_join(AAPI_STEM_WSU, by = "Academic_Start_Year") %>%
  inner_join(Multi_STEM_WSU, by = "Academic_Start_Year") %>%
  inner_join(Hispanic_STEM_WSU, by = "Academic_Start_Year") %>%
  inner_join(Unknown_STEM_WSU, by = "Academic_Start_Year") %>%
  select(Academic_Start_Year, Graduate_STEM, Undergraduate_STEM, black_nodg,
         black_nodug, white_nodug, white_nodg, aapi_nodug, aapi_nodg,
         multi_nodug, multi_nodg, hisp_nodug, hisp_nodg, uk_nodg, uk_nodug)

ggplot(WSU_STEM_degrees_by_race, aes(x = Academic_Start_Year)) +
  geom_line(aes(y = black_nodug, color = "Black")) +
  geom_line(aes(y = white_nodug, color = "White")) +
  geom_line(aes(y = aapi_nodug, color = "AAPI")) +
  geom_line(aes(y = multi_nodug, color = "Multi Racial")) +
  geom_line(aes(y = hisp_nodug, color = "Hispanic")) +
  geom_line(aes(y = uk_nodug, color = "Unknown")) +
  labs(title = "Undergraduate STEM Degrees Granted by Race/Ethnicity at WSU",
       x = "Academic Year",
       y = "Number of Degrees Granted",
       color = "Race/Ethnicity")
```